### 2016-08-29 version0.0/intro0.01.tex
Applying P.W.'s comments on introduction

\section{Prelude}
\label{sec: overview}
%what doIhave inside galaxies:
% stuffIdon't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas.
They all affect each others' formation, evolution, and extinction.
There is also dark matter inside every galaxy, which, to the best of our knowledge, only has gravitational effects on the other components.
Nearly all the information we can obtain from galaxies other than our own comes from their light.
Since each observable phenomenon inside galaxies emits most of its energy in specific wavelengths, 
a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool to understand galaxies. 
Young and evolved stars, dust, and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.

%stars
Arguably, stars are the main component of normal galaxies.
They control the chemical composition and structure of galaxies by transforming gas into new stars and by transforming dead stars back into gas.
They are also central to the formation and evolution of planetary systems.
The energy provided by stars is necessary to create and maintain the life on planets. 
The study of the formation and evolution of the Sun, and more generally that of stars, helps us understand more about our origin and the future of our Solar System.
Furthermore, in order to completely understand the formation and evolution of galaxies from early universe to the current epoch, the knowledge of the formation and evolution of stars is necessary. 
As a result, the study of stellar formation and evolution has been a central topic in astronomy and astrophysics for decades.

%ISM 1)Gas 2)dust
%There could be a galaxy without stars (i.e. dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas. %: this is a very strong statement. Some galaxies, like dwarf ellipticals, are pretty gas-free (at least now). So qualify this a bit. done
Among observable objects in galaxies, gas has a crucial role in formation and evolution of galaxies.
Gas and dust in galaxies can be found in the space between stars.
This space is called the interstellar medium (ISM), and is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
The gas and dust in the ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
The effect of the ISM on stellar formation is undeniable; it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
Studying the interstellar medium is not only essential to understanding the formation of stars, but is also  necessary for interpretation of stellar evolution due to fact that stars release their material into ISM when they reach the end of their evolutionary track.

@@

Molecular clouds in the ISM are cold ($T \sim10$ K) and dense (particle number density $ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses~\citep{Bolato08}.
Density in molecular clouds is not uniform. There are dense and colds clumps inside these clouds.
Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars.
However, H$_2$ molecules, the main component of molecular clouds, have no permanent electric dipole moment which makes them difficult to detect.
The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but these clouds also contain heavier elements such as carbon monoxide, hydrogen cyanide, water, ammonia and more than tens of others.
Carbon monoxide (CO) molecules are the third-most abundant constituent of molecular clouds, and are easily observable.
Other heavier molecules have emission lines which are also detectable in the spectra of clouds (especially Galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds i.e.\ their mass (see Section~\ref{sec: ismmap} for more details).

The molecular clouds are surrounded by clouds of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state. 
The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
The energy of the anti-parallel mode is slightly less than the parallel mode.
Since atoms always want to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
However, the energy difference between these two states is very small and it takes millions of years before the transition happens.
The large amount of hydrogen atoms compensates for the rarity of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
Observation of the \hi atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.

@@

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and have a power-law size distribution.
The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\cite{Peeters04}.
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).

@@

%Most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low energy rotational state}(the state of angular momentum, J) and can be excited in the temperature of molecular clouds. %PB: need to fix text in {\bf} earlier in this sentence.
Most of our knowledge of molecular clouds come from observation of line emission of CO molecules, which, die to their large mass, possess a very low energy rotational state (the state of angular momentum, J) and can be excited in the temperature of molecular clouds. %Sr should I put the \bf back?
Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
Therefore, $^{12}$CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of molecular clouds dominated by molecular hydrogen~\citep[e.g.][]{Sanders84}.
Higher rotational transitions of CO can be used as a tracer as well, but they are not as common as $J(1\rightarrow 0)$.

@@

Giant molecular clouds are self-gravitating systems~\citep[e.g.][]{Efstathiou83,Blitz99}.
Thus, using the virial theorem leads to calculating the mass of the cloud: 
\begin{equation}
 \label{equ: vir}
 M_{cloud} = L_{\rm CO} \sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}},
\end{equation}
where $\rho$ is the mass density of the cloud and $\sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}$ is called the conversion factor.
Equ.~\ref{equ: vir} shows that the total mass of molecular clouds and the CO luminosity of the cloud are directly related~\citep{Young91}. 
Since the dependence of $I_{\mathrm CO}$ on optical depth is negligible~\citep{Krumholz09}, total CO luminosity can be used to measure the total H$_2$ mass of galaxies.
The relation between CO emission and H$_2$ cloud mass is shown to be
\begin{equation}
N_{\rm H_2}/\rm cm^{-2} = X_{\rm CO} \times I_{\rm CO}/{\rm K km s}^{-1},
\end{equation}
where X$_{\rm CO}$ is the conversion factor (also known as the X-factor).
The X-factor is different for each galaxy and sometimes is even different in regions within a galaxy due to differences in properties such as metallicity.
Although assuming a constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity this assumption leads to uncertainties~\citep{Bolato13}. 
Various groups are working on observations of different types of galaxies to measure the X-factor for them~\citep{Wilson95, Bosselli02, Bolato13}.

@@

Atomic gas in galaxies is dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-2}$), along the line-of-sight.
\begin{equation}
N_{H {\sc I}}  \propto \int T_{\mathrm B} dV
\end{equation}
where $T_{\mathrm B}$ is the temperature brightness in Kelvin and dV is in km~s$^{-1}$, with the integral over the line profile. 
These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.

@@

Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical, due to low spatial resolution of available observational data.
\cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin. 
The Herschel Space Telescope \cite{Pilbratt10} has measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. 
This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
The observed FIR flux has almost no dependency on distance, thus, one of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary. 
The other important advantage is that this method solves the newly-found problem of ``dark gas" in galaxies. 
Dark gas is a significant fraction of gas in galaxies which can be traced by neither the 21-cm emission nor the CO emission~\citep{Abdo10}. 
As such, it is very difficult to detect with telescopes, but an accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.

@@

Extinction happens when there is a combination of both absorption and scattering of radiation by dust.
This effect grows inversely with wavelength.
%Extinction can be defined as a reduction of the original intensity caused by dust:
Extinction is quantified as the difference in observed and initial magnitudes of an object in a specific wavelength ($\lambda$):
\begin{equation}
m_{\lambda} - m_{\lambda}(0) = \mathrm{A}_{\lambda},
\end{equation}
where $\mathrm{A}_{\lambda}$ is the extinction, and $m_{\lambda}$ and $m_{\lambda}(0)$ are observed and initial magnitude, respectively.
Magnitude is related to intensity (I) as:
\begin{equation}
m_{\lambda} = 2.5 \log (I_{\lambda}) + C,
\end{equation}
where c is a constant which depends on photometric system that is being used.
Optical depth, $\tau_{\lambda}$, is defined by ratio of observed and initial intensity of a source as:
\begin{equation}
\label{equ: extinction}
{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)\exp[-\tau_{\lambda}],
\end{equation}
where I$(\lambda)$ is observed intensity in wavelength $\lambda$ and I$_0(\lambda)$ is intensity of light before passing through dust.
Therefore, the optical depth and extinction can be converted to one an other by $\tau_{\lambda} = 1.086 \mathrm{A}_{\lambda}$. 
The extinction also depends on the grain size and extinction cross section.
For measuring SFR using various wavebands, decreasing of the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR.

@@

\section{Measuring the star formation rate in galaxies} 
\label{sec: sfr_intro}
Understanding the formation of stars leads to better understanding of galaxies' formation and evolution. 
Characterisation of the star formation processes such as star formation rate (SFR) and the stellar initial mass function (IMF) is necessary in examining galaxies' structure formation~\citep{McKee07}. 
Measuring the SFR is not trivial and depends on a galaxy's morphology, metallicity, IMF, observational spatial resolution, and other properties. 
There is a large number of review papers on how stars form and how their formation is traced. 
From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by~\citep{McKee07}. 
From an observational standpoint, star formation is discussed by \cite[][and references therein]{Kennicutt98b, Kewley02, Calzetti13, Boquien10, Kennicutt12}.

In principle, emission from new stars can be traced by ultraviolet, visible light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission. 
Some of this emission is directly from stars, e.g.\ UV emission, and some is from ISM components that absorb and re-emit light from young stars, e.g.\ far-infrared emission.
Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08} 
Peak of emission of young, hot, and massive stars is in UV wavelength, which makes them an ideal tracer of the current SFR.
One of the main assumptions in using the luminosity of massive stars is that the SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. 
By knowing the IMF, the number of massive stars can be used to extrapolate the total number of stars formed in a given star-forming region.
To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Section~\ref{sec: imf}).
In general each tracer has some systematic errors, and one should decide which tracer is more accurate for a given system.

@@

In the late 1970s, it was recognised that the assumption of a the single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}. 
Since then, many groups have studied the stellar IMF and found different power-law relations (Fig.~\ref{fig: imf} ). 
Most SFR calibrations have the same assumption that the stellar IMF is constant across all environments and adopt it from the standard stellar IMF introduced by\cite{Kroupa01}:
\begin{equation}
\begin{split}
    \Phi (\log M) & \propto M^{-2.3}    \quad    (0.1 \le M(M{\odot}) \le 0.5)\\                  
           & \propto M^{-3.3}    \quad    (0.5 \le M(M{\odot}) \le 100)
\end{split}
\end{equation}
Although the Salpeter IMF produces more low-mass stars than the Kroupa IMF, they produce almost the same number of high-mass stars. 
Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF can be converted to the Salpeter IMF by multiplying the calibration constant by 0.67~\citep{Madau14}.
In a more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMFs overestimate the number of stars with masses greater than 8M$_\odot$.
\cite{Bastin10} reviewed the stellar IMF as derived from many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins especially at the high-mass end.

@@

Another single-band SFR indicator is the emission from hydrogen recombination lines. 
Ionizing photons emitted from young massive stars ionize the surrounding gas. Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ ($0.6563 \mu$m) and H${\beta}$ ($0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators~\citep{Kennicutt98a}. 
The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived using quantum mechanics. 
The assumption is that the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}.
Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorb and re-emit via Ly${\alpha}$ and longer wavelengths.
This is why the H${\alpha}$ emission line strength is greater in optically thick environments. The relation between the SFR, the luminosity of the \halpha emission line, and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
\begin{align}
\label{equ: halpha}
SFR(H\alpha) = 5.5 \times 10^{-42}L(H\alpha) \\
                     = 7.4 \times 10^{-54}Q(H^{\circ})
\end{align}
where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density n$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the \hii~regions.
Dust extinction (Section~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g. by adding L(24~$\mu$m) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.

Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727~\AA. 
Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. 
\cite{Gallagher89} calibrated the SFR based on the \oii luminosity by using a sample of 75 galaxies. 
Another calibration for this luminosity was derived by \cite{Kennicutt92}. 
In his review on the SFR,~\citep{Kennicutt98b} averaged these calibrations and derived the following relation:
\begin{equation}
SFR([O\ II]) = 1.4 \times 10^{-41} L([O\ II])
\end{equation}  
where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\oii) is in erg~s$^{-1}$.
Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high-redshift galaxies.
In these galaxies, the \halpha emission line is redshifted out of the optical band.
Consequently, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is very useful~\citep{Kennicutt98b}.

>>>>

\section{Prelude}
\label{sec: overview}
%what doIhave inside galaxies:
% stuffIdon't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas.
They all affect each others' formation, evolution, and extinction.
There is also dark matter inside every galaxy, which, to the best of our knowledge, only has gravitational effects on the other components.
Nearly all the information we can obtain from galaxies other than our own comes from their light.
Since each observable phenomenon inside galaxies emits most of its energy in specific wavelengths, 
a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool to understand galaxies. 
Young and evolved stars, dust, and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
Therefore, by properly modeling observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.

%stars
Arguably, stars are the main component of normal galaxies.
They control the chemical composition and structure of galaxies by transforming gas into new stars and by transforming dead stars back into gas.
They are also central to the formation and evolution of planetary systems.
The energy provided by stars is necessary to create and maintain the life on planets. 
The study of the formation and evolution of the Sun, and more generally that of stars, helps us understand more about our origin and the future of our Solar System.
Furthermore, in order to completely understand the formation and evolution of galaxies from the early universe to the current epoch, the knowledge of the formation and evolution of stars is necessary. 
As a result, the study of stellar formation and evolution has been a central topic in astronomy and astrophysics for decades.

%ISM 1)Gas 2)dust
%There could be a galaxy without stars (i.e. dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas. %: this is a very strong statement. Some galaxies, like dwarf ellipticals, are pretty gas-free (at least now). So qualify this a bit. done
Among observable objects in galaxies, gas has a crucial role in formation and evolution of galaxies.
Gas and dust in galaxies can be found in the space between stars.
This space is called the interstellar medium (ISM), and is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
The gas and dust in the ISM are heated by interstellar radiation field and cooled through a variety of line and continuum processes which usually depend on the local physical conditions. 
The effect of the ISM on stellar formation is undeniable; it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
Studying the interstellar medium is not only essential to understanding the formation of stars, but is also  necessary for interpretation of stellar evolution due to fact that stars release their material into ISM when they reach the end of their evolutionary track.

@@

Molecular clouds in the ISM are cold ($T \sim10$ K) and dense (particle number density $ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses~\citep{Bolato08}.
Density in molecular clouds is not uniform. There are dense and cold clumps inside these clouds.
Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars.
However, H$_2$ molecules, the main component of molecular clouds, have no permanent electric dipole moment which makes them difficult to detect.
The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but these clouds also contain heavier elements such as carbon monoxide, hydrogen cyanide, water, ammonia and more than tens of others.
Carbon monoxide (CO) molecules are the third-most abundant constituent of molecular clouds, and are easily observable.
Other heavier molecules have emission lines which are also detectable in the spectra of clouds (especially Galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds i.e.\ their mass (see Section~\ref{sec: ismmap} for more details).

The molecular clouds are surrounded by clouds of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state. 
The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
The energy of the anti-parallel mode is slightly less than the parallel mode.
Since atoms always want to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
However, the energy difference between these two states is very small and it takes millions of years before the transition happens.
The large amount of hydrogen atoms compensates for the rarity of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
Observation of the \hi~atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.

@@

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and have a power-law size distribution.
The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).

@@

%Most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low energy rotational state}(the state of angular momentum, J) and can be excited in the temperature of molecular clouds. %PB: need to fix text in {\bf} earlier in this sentence.
Most of our knowledge of molecular clouds come from observation of line emission of CO molecules, which, due to their large mass, possess a very low energy rotational state (the state of angular momentum, J) and can be excited in the temperature of molecular clouds. %Sr should I put the \bf back?
Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
Therefore, $^{12}$CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of molecular clouds dominated by molecular hydrogen~\citep[e.g.][]{Sanders84}.
Higher rotational transitions of CO can be used as a tracer as well, but they are not as common as $J(1\rightarrow 0)$.

@@

Giant molecular clouds are self-gravitating systems~\citep[e.g.][]{Efstathiou83,Blitz99}.
Thus, using the virial theorem leads to calculating the mass of the cloud: 
\begin{equation}
 \label{equ: vir}
 M_{cloud} = \frac{L_{\rm CO}}{T_{\rm CO}} \sqrt{\frac{4\rho}{3\pi G }},
\end{equation}
where $\rho$ is the mass density of the cloud and $\frac{1}{T_{\rm CO}}\sqrt{\frac{4\rho}{3\pi G}}$ is called the conversion factor.
Equ.~\ref{equ: vir} shows that the total mass of molecular clouds and the CO luminosity of the cloud are directly related~\citep{Young91}. 
Since the dependence of $I_{\mathrm CO}$ on optical depth is negligible~\citep{Krumholz09}, total CO luminosity can be used to measure the total H$_2$ mass of galaxies.
The relation between CO emission and H$_2$ cloud mass is shown to be
\begin{equation}
N_{\rm H_2}/\rm cm^{-2} = X_{\rm CO} \times I_{\rm CO}/{\rm K km s}^{-1},
\end{equation}
where X$_{\rm CO}$ is the conversion factor (also known as the X-factor).
The X-factor is different for each galaxy and sometimes is even different in regions within a galaxy due to differences in properties such as metallicity.
Although assuming a constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity this assumption leads to uncertainties~\citep{Bolato13}. 
Various groups are working on observations of different types of galaxies to measure the X-factor for them~\citep{Wilson95, Bosselli02, Bolato13}.

@@

Atomic gas in galaxies is dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-2}$), along the line-of-sight.
\begin{equation}
N_{H {\sc I}}  \propto \int T_{\mathrm B} dV
\end{equation}
where $T_{\mathrm B}$ is the temperature brightness in Kelvin and dV is in km~s$^{-1}$, with the integral over the line profile. 
These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi~is detectable in most spiral galaxies and some elliptical galaxies).
Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.

@@

Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical, due to low spatial resolution of available observational data.
\cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin. 
The Herschel Space Telescope~\citep{Pilbratt10} has measured the continuum dust emission from hundreds of galaxies~\citep{Eales10, Oliver12}. 
This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
The observed FIR flux has almost no dependency on distance, thus, one of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary. 
The other important advantage is that this method solves the newly-found problem of ``dark gas" in galaxies. 
Dark gas is a significant fraction of gas in galaxies which can be traced by neither the 21-cm emission nor the CO emission~\citep{Abdo10}. 
As such, it is very difficult to detect with telescopes, but an accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.

@@

Extinction happens when there is a combination of both absorption and scattering of radiation by dust.
This effect grows inversely with wavelength.
%Extinction can be defined as a reduction of the original intensity caused by dust:
Extinction is quantified as the difference in observed and initial magnitudes of an object in a specific wavelength ($\lambda$):
\begin{equation}
m_{\lambda} - m_{\lambda}(0) = \mathrm{A}_{\lambda},
\end{equation}
where $\mathrm{A}_{\lambda}$ is the extinction, and $m_{\lambda}$ and $m_{\lambda}(0)$ are observed and initial magnitude, respectively.
Magnitude is related to intensity (I) as:
\begin{equation}
m_{\lambda} = 2.5 \log (I_{\lambda}) + C,
\end{equation}
where $c$ is a constant which depends on photometric system that is being used.
Optical depth, $\tau_{\lambda}$, is defined by ratio of observed and initial intensity of a source as:
\begin{equation}
\label{equ: extinction}
{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)\exp[-\tau_{\lambda}],
\end{equation}
where I$(\lambda)$ is observed intensity in wavelength $\lambda$ and I$_0(\lambda)$ is intensity of light before passing through dust.
Therefore, the optical depth and extinction can be converted to one an other by $\tau_{\lambda} = 1.086 \mathrm{A}_{\lambda}$. 
The extinction also depends on the grain size and extinction cross section.
For measuring SFR using various wavebands, decreasing of the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR.

@@

\section{Measuring the star formation rate in galaxies} 
\label{sec: sfr_intro}
Understanding the formation of stars leads to better understanding of galaxies' formation and evolution. 
Characterisation of the star formation processes such as star formation rate (SFR) and the stellar initial mass function (IMF) is necessary in examining galaxies' structure formation~\citep{McKee07}. 
Measuring the SFR is not trivial and depends on a galaxy's morphology, metallicity, IMF, observational spatial resolution, and other properties. 
There is a large number of review papers on how stars form and how their formation is traced. 
From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by~\cite{McKee07}. 
From an observational standpoint, star formation is discussed by many authers \citep[e.g.][and references therein]{Kennicutt98b, Kewley02, Calzetti13, Boquien10, Kennicutt12}.

In principle, emission from new stars can be traced by ultraviolet, visible light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission. 
Some of this emission is directly from stars, e.g.\ UV emission, and some is from ISM components that absorb and re-emit light from young stars, e.g.\ far-infrared emission.
Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08}. 
Peak of emission of young, hot, and massive stars is in UV wavelength, which makes them an ideal tracer of the current SFR.
One of the main assumptions in using the luminosity of massive stars is that the SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. 
By knowing the IMF, the number of massive stars can be used to extrapolate the total number of stars formed in a given star-forming region.
To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Section~\ref{sec: imf}).
In general each tracer has some systematic errors, and one should decide which tracer is more accurate for a given system.

@@

In the late 1970s, it was recognised that the assumption of a the single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}. 
Since then, many groups have studied the stellar IMF and found different power-law relations (Fig.~\ref{fig: imf} ). 
Most SFR calibrations have the same assumption that the stellar IMF is constant across all environments and adopt it from the standard stellar IMF introduced by\ \cite{Kroupa01}:
\begin{equation}
\begin{split}
    \Phi (\log M) & \propto M^{-2.3}    \quad    (0.1 \le M(M{\odot}) \le 0.5)\\                  
           & \propto M^{-3.3}    \quad    (0.5 \le M(M{\odot}) \le 100)
\end{split}
\end{equation}
Although the Salpeter IMF produces more low-mass stars than the Kroupa IMF, they produce almost the same number of high-mass stars. 
Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF can be converted to the Salpeter IMF by multiplying the calibration constant by 0.67~\citep{Madau14}.
In a more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMFs overestimate the number of stars with masses greater than 8M$_\odot$.
\cite{Bastin10} reviewed the stellar IMF as derived from many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins especially at the high-mass end.

@@

Another single-band SFR indicator is the emission from hydrogen recombination lines. 
Ionizing photons emitted from young massive stars ionize the surrounding gas. Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ ($0.6563 \mu$m) and H${\beta}$ ($0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators~\citep{Kennicutt98a}. 
The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived using quantum mechanics. 
The assumption is that the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}.
Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorb and re-emit via Ly${\alpha}$ and longer wavelengths.
This is why the H${\alpha}$ emission line strength is greater in optically thick environments. The relation between the SFR, the luminosity of the \halpha\ emission line, and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
\begin{align}
\label{equ: halpha}
SFR(H\alpha) = 5.5 \times 10^{-42}L(H\alpha) \\
                     = 7.4 \times 10^{-54}Q(H^{\circ})
\end{align}
where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density n$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the \hii~regions.
Dust extinction (Section~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
The effects of dust must be measured and \halpha\ observations must be corrected for extinction (e.g. by adding lumincity at 24~$\mu$m (L(24~$\mu$m)) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
